---
title: "Shiny App Covid"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Shiny App Covid}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CovidShiny)
```


The goal of CovidShiny is to present the user the evolution of the pandemic related to COVID-19 across the world. 
We do it using a Shiny web app that contains the following elements: 
* stacked plotlys bars 
* a dot density map and a table. 
There are many ways the user can interact with the App to find relevant information:
  1. Dot Density Map: With a slider the user can choose the dates from the dot-density map and see in each day of 2020 how was the spread of the virus across the world.
  2. Dot Density Map: With buttons the user can choose if we wants to see the dot density map in relative or absolute terms (divided by 1 million habs).
  3. Table: With a slider the user can choose dates and see what were the 10 countries that suffered the most in each day according to new cases of Covid.


